---
title: "Nonlinear Portfolio Optimization"
author: 'Team 12: Ben Silverberg, Ryan Lee, Andrew Lagattuta, Selena Smith'
date: "12/9/2022"
output: pdf_document
---

```{r load-packages, include=FALSE}
library(dplyr)
library(magrittr)
library(knitr)
library(tidyverse)
library(RMySQL)
library(reshape2)
library(tinytex)
```


```{r}

#Connect to MySQL
pwd <- .rs.askForPassword("DB Password:")
con <- RMySQL::dbConnect(RMySQL::MySQL(),dbname='nasdaq', username='root', password=pwd)
```


```{r}
#Metadata
dbListTables(con)

port_db <- tbl(con, 'portfolio')
port_query <- port_db %>%
  select(expReturn, expRisk)

port_query %>% show_query()

dbGetQuery(con, '
SELECT *
FROM portfolio
')
```

```{r}
# plot the (x,y) values from the portfolio table onto a graph

ggplot(data = port_db, aes(.data$expReturn, .data$expRisk)) +
    geom_point() +
    labs(x = "Expected Return", y = "Expected Risk", title = "Nasdaq Portfolio of Expected Risk vs. Expected Return")

dbDisconnect(con)
```

## Commentary

In this assignment, we used R, MySQL, Gurobi, Python, Excel, and Solver as an 
integrated toolkit to help a user select a portfolio of NASDAQ stocks that
maximizes returns for several different levels of risk.

The following deliverables are submitted for consideration:

• portfolio.py - Python program.
• calc_corr.R - R program to populate the covariance or correlation matrix.
• nasdaq.sql - Final database dump (export).
• writeup.Rmd - The R Notebook used to generate this write up.
• writeup.PDF - PDF knitted from the R notebook consisting of the graph.

An Excel Solver prototype was generated to solve the given simple portfolio 
maximization problem; the same model was then built in Gurobi to validate our results. 

A NASDAQ database was then created in MySQL to support our R and Python programs.

R was used to calculate the required matrix, vector, and to load the matrix of 10 
year NASDAQ monthly returns to look at the mean of each stock and populate tables
as required. 

Python was used to generate the objective function terms and constraints, as appropriate, 
using the values from your Solver prototype.

Finally, the (x,y) values were read from the portfolio table, and plotted here. 

In this graph, the expected return rises gradually as the expected risk
increases until it reaches a steady state at about 0.27 for an expected risk of
about 0.6 and above.
